% !TEX program = xelatex

\documentclass{resume}
\usepackage{graphicx}
\usepackage{tabu}
\usepackage{multirow}

\usepackage{geometry}
 \geometry{
 a4paper, 
 total={170mm, 257mm}, 
 left=2mm, 
 right=2mm, 
 top=1mm, 
 bottom=0.5mm
 }

%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number
\newcommand{\changeurlcolor}[1]{\hypersetup{urlcolor=#1}}      
\large{
  \begin{tabu}{l r }
    \scshape{\huge{Jian Wang}} & \hspace{2cm}  \pbar{C++}{0.95} \\
     \email {wangjian790@gmail.com} &  \hspace{2cm} \pbar{Java}{0.9} \\
     \phone{(+1) 850-443-5826} & \hspace{2cm}\pbar{Python}{0.9} \\
     \faUser \ \changeurlcolor{blue}\href{https://wangjian790.github.io/jianwang.github.io/}{https://wangjian790.github.io/jianwang.github.io/} &   \hspace{2cm}\pbar{Linux}{0.8} \\
     \faGithub\ \changeurlcolor{blue}\href{https://github.com/wangjian790/}{https://github.com/wangjian790/} & \hspace{2cm}  \pbar{Latex}{0.8}\\
     \faLinkedin\ \changeurlcolor{blue}\href{https://www.linkedin.com/in/jian-wang-9b476617/}{https://www.linkedin.com/in/jian-wang-9b476617/} &  \hspace{2cm} \pbar{Matlab}{0.8}

  \end{tabu}
}


\section{\faThumbsOUp\ Strength and objective:}\large 
 Financial math Ph.D. with three years quantitative and research working experience in insurance and securities companies. Strong C++, Java and Python skills. Proficient in machine learning, mathematics, and programming. Currently seeking quantitative jobs in buy-side companies. 

\section{\faGraduationCap\ Education}\large 
\datedsubsection{\textbf{FLORIDA STATE UNIVERSITY},  Tallahassee,  FL,  USA}{2011 -- 2017}
\textit{Ph.D.} in financial mathematics\\
Thesis: \textit{Ensemble methods for capturing dynamics of limit order books}\\
Advisor: \textit{Dr.Jinfeng Zhang (Statistics) and Dr. Giray $\ddot{O}$kten(Financial mathematics)} 
\datedsubsection{\textbf{FLORIDA STATE UNIVERSITY},  Tallahassee,  FL,  USA}{2009 -- 2011}
\textit{Master} of financial mathematics,  GPA : 3.6/4.0
\datedsubsection{\textbf{Shanghai University}, joint training master with Fudan-AIA actuarial center, Shanghai,  China}{1998 -- 2005}
\textit{Bachelor and Master} in mathematics,  GPA : 3.4/4.0
\section{\faGears\ Experience}
\datedsubsection{\textbf{EVERBRIGHT SECURITIES CO.,  LTD.}
	Shanghai,  China}{06/2013 -- 09/2013}
\large \role{Fixed Income Summer Intern, }{Manager: Yan Wei Gao}
\begin{itemize}\large
	\item Position analysis for US treasury futures via the data from CFTC website,  analyze the trading strategy for PIMCO. Seeking arbitrage opportunities for US Treasury futures. Co-Wrote and provided a research report to buy-side companies.  
\end{itemize}
\datedsubsection{\textbf{REWARD HEALTH INSURANCE CO., LTD., }
 Shanghai,  China}{07/2008 -- 05/2009}
\large \role{Quantitative associate, }{Manager: Wei Wei}
\begin{itemize}\large
  \item Developed the premiums for life insurance product by EXCEL and VBA. Conducted sensitivity test and scenario test of the profit of insurance products. Defined the commission rate and expense rate. 
  
  
\end{itemize}

\datedsubsection{\textbf{SINO-LIFE INSURANCE CO., LTD., }
 Shanghai,  China}{07/2005 -- 07/2008}
\large \role{Quantitative analyst, }{Manager: Xiuwen Wang}
\begin{itemize}\large
  \item Defined the commission rates and appropriate budgets for insurance products based on the ROI,  ROC, and profit margin. Conducted profit test,  sensitivity test and scenario test to ensure the product feasibility in the market. Calculated the premium,  reserve and cash value for insurance products based on benefit-contribution-parity principle.
\end{itemize}
\section{\faBook\ Research}

\begin{itemize}[parsep=0.5ex]\large
  \item Albert Steppi, Jinchan Qu, Jie Hao, \textbf{Jian Wang}. Mining protein interactions affected by mutations using a NLP based machine learning approach. \textit{The six Biocreative text mining workshop}, 2017(accepted).
  \item \textbf{Jian Wang}, Jinfeng Zhang and Giray $\ddot{O}$kten. Ensemble methods for capturing dynamics of limit order books. \textit{Florida University Ph.D. dissertation thesis(accepted) and Journal of High Frequency(submitted)} 2017.
  \item Yuchu Lu, Qian Wang, \textbf{Jian Wang}. A risk analysis model in medical insurance. \textit{The 8th Annual Conference paper} 2004 
  
\end{itemize}
    
\section{\faWrench
\ Skills}
\begin{itemize}[parsep=0.5ex]\large
  \item \textbf{Computer:} More than 4 years C++(Class,  Inheritance,  Polymorphism,  Template,  STL,  etc) and python( Numpy,  Pandas, 
  Sklearn,  Tensorflow,  etc) programming experience in research, proficient in java, R, algorithm, and data structures. Projects experience with Linear regression, Logistic regression, Boosting methods and Deep neural networks.  Projects experience with Big Data/Hadoop MapReduce and Spark system. 
  
  \item \textbf{Mathematics:}
   Linear regression, Generalized linear model, Measure and Integral,  Distribution theory, Statistical inference, Convexity optimization, Stochastic calculus, Linear algebra and matrix computations. 
  
\end{itemize}

\section{\faShirtsinbulk \ Certificates}\large 
Deep learning.ai certificate(four courses); Machine learning certificate(four courses); Lynda Become a C++ Developer certificate. Lynda C++ Essential Training certification.

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
